```{r}
library(readxl)
library(dplyr)

customers <- read_excel("C:\\Users\\Lakshi\\Desktop\\customer_data.xlsx", sheet =1)
glimpse(customers)
```
Thus the data has 999 rows and 5 columns. It gives information about the customers, the industries in which they deal along with their sales method and language.
```{r}
#To check for uniqueness
length(unique(data_my$id_m))
```
Therefore the dataset contains data about 999 customers.
```{r}
Prod_type <- read_excel("C:\\Users\\Lakshi\\Desktop\\customer_data.xlsx", sheet =2)
glimpse(Prod_type)
```
Thus the data has 1457 rows and 4 columns. It contains information about product and its validity indicated by its beginning date and end date.
```{r}
table(Prod_type$product)
```
There are two types of product Credit Card Acceptance and Terminal.
```{r}
trx_data =  read.csv("C:\\Users\\Lakshi\\Desktop\\trx_data.csv" )
glimpse(trx_data)
```
The transaction data consists of transaction details of customers including transaction amount along with year and month of transaction data. 
```{r}
trx_data %>% distinct(trx_year)
```
Therefore it contains transaction data for year 2020 only.
```{r}
length(unique(trx_data$merchant))
```
The dataset contains 761 unique customer ids.

Lets look at the active customers.
```{r}
Prod_type$active = case_when(as.Date(Prod_type$enddate)>=Sys.Date()~1,TRUE~0)
glimpse(Prod_type)
```

```{r}
#Making Pivot tables
library("reshape2")
Active_customers =dcast(Prod_type,id_merchant~product,value.var = "active",fun.aggregate = sum)
colnames(Active_customers)[2] = "Creditcard_Acceptance"
Active_customers
```

```{r}
Active_customers
```
```{r}
table(Active_customers$Creditcard_Acceptance)
```
```{r}
table(Active_customers$Terminal)
```


```{r}
#Active customers for both products
both =  Active_customers %>%
        select(id_merchant,Creditcard_Acceptance , Terminal) %>%
        filter(Creditcard_Acceptance >=1 & Terminal >=1)
both
```

```{r}
both%>%distinct(id_merchant)
```
391 customers have both credit card acceptance and terminal product.

```{r}
CCA_customers =  Active_customers %>%
        select(id_merchant,Creditcard_Acceptance , Terminal) %>%
        filter(Creditcard_Acceptance >=1)
CCA_customers %>% distinct(id_merchant)
```
868 customers have credit card acceptance product.
```{r}
Terminal_customers =  ptq %>%
        select(id_merchant,Creditcard_Acceptance , Terminal) %>%
        filter(Terminal >=1)
Terminal_customers %>%distinct(id_merchant)
```

521 customers have terminal cards.
```{r}
Atleast_oneproduct = 868+521-391
Atleast_oneproduct
```

Thus, according to set theory:
Customers with atleast one product = 885 + 521 - 391  = 998

Exactly one product 
```{r}
#Terminal Product only
Terminal_only =  Active_customers %>%
        select(id_merchant,Creditcard_Acceptance , Terminal) %>%
        filter(Terminal >=1 & Creditcard_Acceptance ==0)
Terminal_only %>%distinct(id_merchant)
```
130 customers have terminal product only.
```{r}
#Credit Card Product Only
CCP_only =  Active_customers %>%
        select(id_merchant,Creditcard_Acceptance , Terminal) %>%
        filter(Creditcard_Acceptance >=1 & Terminal ==0 )
Active_customers %>%distinct(id_merchant)
```
477 customers have credit card acceptance only.

```{r}
#Average Transaction Amount per industry
trx_industry = merge(customers,trx_data,by.x = 'id_m', by.y = 'merchant')
#trx_industry
glimpse(trx_industry)

```
```{r}

pt9 = trx_industry %>% group_by(industry)%>%summarise(avg_trx_amount = mean(trx_amount))
pt9
```
```{r}
library(ggplot2)
ggplot(pt9,aes(industry, avg_trx_amount,fill = industry))+ geom_bar(stat= 'identity') 
```
